Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-14 thesis/thesis.tex
thesis: Review Results

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/melotte_22/features_melotte_22.png}
  \end{subfigure}
  \caption{Melotte 22 feature pairplot}
  % TODO: Ampliar la descripción de la figura
  \label{fig:features_melotte_22}
\end{figure}

@@

@@

\begin{minted}{python}
  n_clusters, kmeans = estimate_n_clusters(melotte22_df,
                                           min_clusters=3, max_clusters=7)
  # Output
  # Silhouette score for 3 clusters: 0.5420
  # Silhouette score for 4 clusters: 0.5393
  # Silhouette score for 5 clusters: 0.5608
  # Silhouette score for 6 clusters: 0.5336
  # Silhouette score for 7 clusters: 0.5306
  # Best silhouette score is 0.5608 for 5 clusters
\end{minted}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr}\tablefootnote{Results have been taken from \protect\citeA[p.~25. Table A.3. Pleiades]{babusiaux2018gaia}} &
        19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      Clusterix+TOPCAT & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 35.16 & -38.01 $\pm$ 40.16 & 7.23 $\pm$ 2.35 & 1378 \\
      DEC & 23.67 $\pm$ 38.33 & -46.23 $\pm$ 44.54 & 8.04 $\pm$ 2.59 & 878 \\
      \textbf{DEC (filtered)} & 19.50 $\pm$ 8.59 & -44.23 $\pm$ 8.17 & 7.42 $\pm$ 0.1 & 438 \\
    \end{tabular}
    \caption{Melotte 22. The parameters shown are proper motion in right ascension and declination, parallax and number of stars with their respective deviations.}
    \label{tab:results_melotte_22}
  \end{center}
\end{table}

@@

We have seen in the previous chapter that the DEC model is capable of refining the clustering selection made by K-Means
hence helping us have a more precise characterization of the cluster.
Now, in order to validate our model and be able to estimate how good or bad it is,
we need a different method to characterize the studied clusters and compare our results with the validation method.

@@

The aim of this section is to highlight the procedure differences between our method and this new one,
as well as using the results provided by this method to validate ours results.
This validation method uses a combination of VO tools: Clusterix 2.0 + TOPCAT.
We take Melotte 22 again as our study case to make easier comparisons between the method presented in Chapter \ref{chap:method}
and this alternative one.

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/clusterix/clusterix_selection_panel_melotte_22.png}
  \end{subfigure}
  \caption{Clusterix 2.0 selection panel with Melotte 22 settings.
           The coordinates correspond to the center of Melotte 22 cluster,
           while the radius is the value registered for this cluster in the
           OpenClust catalogue multiplied by 1.5 (as explained in \ref{sec:data_mining})}
  \label{fig:clusterix_selection}
\end{figure}

This panel allows us to select a region by its coordinates or by searching a cluster by its name in the Gaia DR2 catalogue,
as well as specify the size of the region by introducing its radius.
We can also set limit values in magnitude (for both minimum and maximum) to discard stars outside these limits.
Another setting is the flag to enable or disable the \emph{Q-Filter}.
This filter discards those stars with \emph{null} values in relevant fields.

Clusterix returns a position map for the downloaded stars from Gaia DR2 database using Aladin \cite{bonnarel2000aladin} as an atlas of the sky
(See Figure \ref{fig:aladin_melotte_22}).
At this point, we can choose sending the recovered data to TOPCAT or Aladin, or continue to the next step of this assistant.

@@

It is necessary to remark the importance of this step, since the selection of these regions is critical to get a good result.
However, despite how crucial is this selection, there is no general rule to define these regions.
We only have two references: the radius of the downloaded region and the estimated size for the open cluster that sets the \emph{inner radius}.
The other two radius must be set by trial and error. In general, they should be large enough to be sure we are not taking polluted regions.
This is a tedious process that requires several tries before achieving good enough probability values.

@@

This makes the selection process an art rather than a science, not to mention the required previous knowledge on certain profiles of the
objects to characterize. This puts into question the non-parametric character of the method.

@@

Once data is available in TOPCAT, we have to carefully analyze the imported data.
From there, we can perform a first star selection by excluding those stars with probability value lower than 0.8.
This first result can be taken as a good starting point, but we still need to make some fine tunning.
As we can see in Figure \ref{fig:topcat_prob_selection_melotte_22}, the selection is too restrictive and we have lost too many stars.

@@

Taken these observations into account, we can proceed to make a new selection based on parallax properties.
Our second selection makes use of the values obtained with the previous selection for parallax and its standard deviation and
selects those stars from the whole set which fall inside the limits $7.304mas \pm 0.797$ (see Figure \ref{fig:topcat_parallax_melotte_22}).

@@

For the sake of completeness, Table \ref{tab:results_melotte_22} is shown again,
in order to compare the results obtained with the validation method and our method.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & 19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      \textbf{Clusterix+TOPCAT} & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 35.16 & -38.01 $\pm$ 40.16 & 7.23 $\pm$ 2.35 & 1378 \\
      DEC & 23.67 $\pm$ 38.33 & -46.23 $\pm$ 44.54 & 8.04 $\pm$ 2.59 & 878 \\
      DEC (filtered) & 19.50 $\pm$ 8.59 & -44.23 $\pm$ 8.17 & 7.42 $\pm$ 0.1 & 438 \\
    \end{tabular}
  \end{center}
\end{table}

@@

The majority of the runnings have taken a few minutes, while big clusters such as Melotte 25, have taken around an hour to perform
the computations. This contrasts with \citeA{castro2020hunting} work, that used the power of the MareNostrum 42 supercomputer in order
to perform its calculations.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -4.6579 $\pm$ 0.0075 & 11.1517 $\pm$ 0.0075 & 2.4118 $\pm$ 0.0006 & 1727 \\
      Clusterix+TOPCAT & -4.652 $\pm$ 0.523 & 11.203 $\pm$ 0.454 & 2.409 $\pm$ 0.127 & 638 \\
      KMeans & -4.344 $\pm$ 5.670 & 9.507 $\pm$ 7.546 & 2.268 $\pm$ 0.288 & 1542 \\
      DEC & -4.426 $\pm$ 6.529 & 9.952 $\pm$ 8.018 & 2.436 $\pm$ 0.358 & 1532 \\
      \textbf{DEC (filtered)} & -4.502 $\pm$ 4.46 & 10.114 $\pm$ 5.719 & 2.392 $\pm$ 0.135 & 1072 \\
    \end{tabular}
    \caption{NGC 2516 results.}
    \label{tab:results_ngc_2516}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
      Clusterix+TOPCAT & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
      KMeans & -26.352 $\pm$ 20.562 & -15.828 $\pm$ 19.152 & 5.394 $\pm$ 0.696 & 629 \\
      DEC & -20.012 $\pm$ 20.657 & -14.742 $\pm$ 17.330 & 4.686 $\pm$ 0.855 & 894 \\
      \textbf{DEC (filtered)} & -21.571 $\pm$ 19.825 & -14.234 $\pm$ 16.388 & 4.719 $\pm$ 0.706 & 714 \\
    \end{tabular}
    \caption{NGC 2632 results.}
    \label{tab:results_ngc_2632}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -10.9737 $\pm$ 0.0064 & -2.9396 $\pm$ 0.0063 & 1.1325 $\pm$ 0.0011 & 1194 \\
      Clusterix+TOPCAT & -10.970 $\pm$ 0.322 & -2.958 $\pm$ 0.327 & 1.142 $\pm$ 0.080 & 649 \\
      KMeans & -8.616 $\pm$ 5.591 & -3.710 $\pm$ 6.067 & 1.196 $\pm$ 0.226 & 1374 \\
      DEC & -8.926 $\pm$ 5.278 & -3.550 $\pm$ 5.425 & 1.144 $\pm$ 0.159 & 1238 \\
      \textbf{DEC (filtered)} & -9.619 $\pm$ 4.112 & -3.317 $\pm$ 3.976 & 1.140 $\pm$ 0.089 & 990 \\
    \end{tabular}
    \caption{NGC 2682 results.}
    \label{tab:results_ngc_2682}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 11 \\
      Clustering Layer & $\left[ 50, 50, 80 \right]$ \\
      Kernel Initializer Seed & 11 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{Melotte 25 DEC model hyperparameters.}
    \label{tab:hyperparameters_melotte_25}
  \end{center}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & 104.92 $\pm$ 0.12 & -28.00 $\pm$ 0.09 & 21.052 $\pm$ 0.065 & - \\
      Clusterix+TOPCAT & 106.796 $\pm$ 6.229 & -24.870 $\pm$ 5.417 & 21.210 $\pm$ 1.115 & 109 \\
      KMeans & 81.410 $\pm$ 71.475 & -45.309 $\pm$ 73.945 & 21.056 $\pm$ 6.018 & 365 \\
      DEC & x $\pm$ x & x $\pm$ x & x $\pm$ x & x \\
      \textbf{DEC (filtered)} & x $\pm$ x & x $\pm$ x & x $\pm$ x & x \\
    \end{tabular}
    \caption{Melotte 25 results.}
    \label{tab:results_melotte_25}
  \end{center}
\end{table}

@@

All of these clusters have a wide variety of diameters, from 25 to 330 arcmin, as well as the number of stars that belong to them.
NGC 2682 has 3,000 stars while Melotte 25 is composed by more than 400,000 stars.

% TODO: Meter una tabla con los parámetros de los clusters mencionados

% TODO: Determinar correctamente los errores en las medidas y mencionarlos

In all cases, the model has resolved properly the identity of the cluster and has characterized the membership stars,
giving results compatible with the ones obtained with classic procedures and VO tools.

Compared with the mentioned tools, our model can be fully calified as a non-parameterized model since it does not depend on parameters referred
to the clusters itself but only hyperparameters such as the initial number of clusters to find, or the structure of the Clustering Layer used by DEC model.

Our model is also non-supervised since we do not need to tell the model which stars belong to the cluster or assit it while is training.

Only at the end of the characterization, a fine tunning driven by the user, can be applied in orther to improve the selection by discarding those
stars which fall outside the given quantiles.

In any case we make assumptions about the cluster profile, something that we have to take into account when using VO tools.
This is another evidence that our model is non-parameterized.

>>>>

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/melotte_22/features_melotte_22.png}
  \end{subfigure}
  \caption{Pairwise relationships among variables using Melotte 22 data}
  \label{fig:features_melotte_22}
\end{figure}

@@

Figure \ref{fig:features_melotte_22} shows a pairwise relationship among some features available
in the dataset for Melotte 22 data.
The diagonal of the grid shows the marginal distribution of the data in each column.
This plot can be useful to find correlations between pairs of variables or
to identify resonances in certain variables such as those in the parallax feature.

@@

\begin{minted}{python}
  n_clusters, kmeans = estimate_n_clusters(melotte22_df,
                                           min_clusters=3, max_clusters=7)
  # Silhouette score for 3 clusters: 0.5420
  # Silhouette score for 4 clusters: 0.5393
  # Silhouette score for 5 clusters: 0.5608
  # Silhouette score for 6 clusters: 0.5336
  # Silhouette score for 7 clusters: 0.5306
  # Best silhouette score is 0.5608 for 5 clusters
\end{minted}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr}\tablefootnote{Results have been taken from \protect\citeA[p.~25. Table A.3. Pleiades]{babusiaux2018gaia}} &
        19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      Clusterix+TOPCAT & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 35.16 & -38.01 $\pm$ 40.16 & 7.23 $\pm$ 2.35 & 1378 \\
      DEC & 23.67 $\pm$ 38.33 & -46.23 $\pm$ 44.54 & 8.04 $\pm$ 2.59 & 878 \\
      \textbf{DEC (filtered)} & 19.50 $\pm$ 8.59 & -44.23 $\pm$ 8.17 & 7.42 $\pm$ 0.1 & 438 \\
    \end{tabular}
    \caption{Parameters shown are proper motion in right ascension and declination, parallax
             with their respective deviations and number of stars corresponding to Melotte 22 data.}
    \label{tab:results_melotte_22}
  \end{center}
\end{table}

@@

We have seen in the previous chapter that DEC model is capable
of refining the clustering selection made by K-Means
hence helping us have a more precise characterization of the cluster.
Now, in order to validate our model and to be able to estimate how good or bad it is,
we need a different technique to characterize the studied clusters and compare our results
with those obtained with the validation method.

@@

The aim of this section is to highlight the procedure differences between our method and the validation one,
as well as using the results provided by the second technique to validate ours results.
This validation method uses a combination of VO tools: \emph{Clusterix 2.0 + TOPCAT}.
We take Melotte 22 again as our study case to make easier the comparison process between
the method presented in Chapter \ref{chap:method} and the alternative one.

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/clusterix/clusterix_selection_panel_melotte_22.png}
  \end{subfigure}
  \caption{Clusterix 2.0 selection panel with Melotte 22 settings.
           Coordinates correspond to the center of Melotte 22 cluster,
           while the radius is the value registered for this cluster in the
           OpenClust catalogue multiplied by 1.5 (as explained in \ref{sec:data_mining})}
  \label{fig:clusterix_selection}
\end{figure}

This panel allows us to select a region by its coordinates
or by searching a cluster by its name in the Gaia DR2 catalogue,
as well as to specify the size of the region by introducing its radius.
We can also set limit values in magnitude (for both minimum and maximum)
to discard stars outside these limits.
Another setting is the flag to enable or disable the \emph{Q-Filter}.
This filter discards those stars with \emph{null} values in relevant fields.

Clusterix returns a position map for the downloaded stars from Gaia DR2 database
using Aladin \cite{bonnarel2000aladin} as an atlas of the sky (See Figure \ref{fig:aladin_melotte_22}).
At this point, we can choose sending the recovered data to TOPCAT or Aladin,
or continue to the next step of the assistant.

@@

It is necessary to remark the importance of this step,
since the selection of these regions is critical to get a good result.
However, despite how crucial this step is, there is no general rule to define these regions.
We only have two references:
the radius of the downloaded region and the estimated size for the OC that sets the \emph{inner radius}.
The other two radius must be set by trial and error.
In general, they should be large enough to be sure that we are not taking polluted regions.
This is a tedious process and requires several tries before achieving good enough probability values.

@@

This makes the selection process an art rather than a science,
not to mention the required previous knowledge on certain profiles of the objects to characterize.
This puts into question the \emph{non-parameterized} character of the validation method.

@@

Once data is available in TOPCAT, we have to carefully analyze the imported data.
At this point, we can perform a first stars selection by excluding those stars with probability value lower than 0.8.
This first result can be taken as a good starting point, but we still need to make some fine tunning.
As we can see in Figure \ref{fig:topcat_prob_selection_melotte_22},
the selection is too restrictive and we have lost too many stars.

@@

Taking these observations into account,
we can proceed to make a new selection based on parallax properties.
Our second selection makes use of the values obtained with the previous selection
for parallax and its standard deviation and selects those stars from the whole set
which fall inside the limits $7.304mas \pm 0.797$ (see Figure \ref{fig:topcat_parallax_melotte_22}).

@@

For the sake of completeness, Table \ref{tab:results_melotte_22} is shown again.
This table summarizes the results obtained with the validation technique and our method.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & 19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      \textbf{Clusterix+TOPCAT} & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 35.16 & -38.01 $\pm$ 40.16 & 7.23 $\pm$ 2.35 & 1378 \\
      DEC & 23.67 $\pm$ 38.33 & -46.23 $\pm$ 44.54 & 8.04 $\pm$ 2.59 & 878 \\
      DEC (filtered) & 19.50 $\pm$ 8.59 & -44.23 $\pm$ 8.17 & 7.42 $\pm$ 0.1 & 438 \\
    \end{tabular}
  \end{center}
\end{table}

@@

The majority of the runnings have taken a few minutes, while big clusters such as Melotte 25,
have taken around an hour to perform the computations.
This contrasts with \citeA{castro2020hunting} work,
that used the power of the MareNostrum 42 supercomputer in order to perform its computations.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -4.6579 $\pm$ 0.0075 & 11.1517 $\pm$ 0.0075 & 2.4118 $\pm$ 0.0006 & 1727 \\
      Clusterix+TOPCAT & -4.652 $\pm$ 0.523 & 11.203 $\pm$ 0.454 & 2.409 $\pm$ 0.127 & 638 \\
      KMeans & -4.344 $\pm$ 5.670 & 9.507 $\pm$ 7.546 & 2.268 $\pm$ 0.288 & 1542 \\
      DEC & -4.426 $\pm$ 6.529 & 9.952 $\pm$ 8.018 & 2.436 $\pm$ 0.358 & 1532 \\
      \textbf{DEC (filtered)} & -4.502 $\pm$ 4.46 & 10.114 $\pm$ 5.719 & 2.392 $\pm$ 0.135 & 1072 \\
    \end{tabular}
    \caption{NGC 2516 results.}
    \label{tab:results_ngc_2516}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
      Clusterix+TOPCAT & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
      KMeans & -26.352 $\pm$ 20.562 & -15.828 $\pm$ 19.152 & 5.394 $\pm$ 0.696 & 629 \\
      DEC & -20.012 $\pm$ 20.657 & -14.742 $\pm$ 17.330 & 4.686 $\pm$ 0.855 & 894 \\
      \textbf{DEC (filtered)} & -21.571 $\pm$ 19.825 & -14.234 $\pm$ 16.388 & 4.719 $\pm$ 0.706 & 714 \\
    \end{tabular}
    \caption{NGC 2632 results.}
    \label{tab:results_ngc_2632}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -10.9737 $\pm$ 0.0064 & -2.9396 $\pm$ 0.0063 & 1.1325 $\pm$ 0.0011 & 1194 \\
      Clusterix+TOPCAT & -10.970 $\pm$ 0.322 & -2.958 $\pm$ 0.327 & 1.142 $\pm$ 0.080 & 649 \\
      KMeans & -8.616 $\pm$ 5.591 & -3.710 $\pm$ 6.067 & 1.196 $\pm$ 0.226 & 1374 \\
      DEC & -8.926 $\pm$ 5.278 & -3.550 $\pm$ 5.425 & 1.144 $\pm$ 0.159 & 1238 \\
      \textbf{DEC (filtered)} & -9.619 $\pm$ 4.112 & -3.317 $\pm$ 3.976 & 1.140 $\pm$ 0.089 & 990 \\
    \end{tabular}
    \caption{NGC 2682 results.}
    \label{tab:results_ngc_2682}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 9 \\
      Clustering Layer & $\left[ 50, 50, 80 \right]$ \\
      Kernel Initializer Seed & 11 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{Melotte 25 DEC model hyperparameters.}
    \label{tab:hyperparameters_melotte_25}
  \end{center}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & 104.92 $\pm$ 0.12 & -28.00 $\pm$ 0.09 & 21.052 $\pm$ 0.065 & - \\
      Clusterix+TOPCAT & 106.796 $\pm$ 6.229 & -24.870 $\pm$ 5.417 & 21.210 $\pm$ 1.115 & 109 \\
      KMeans & 79.380 $\pm$ 71.691 & -45.314 $\pm$ 73.366 & 20.866 $\pm$ 6.029 & 376 \\
      DEC & 76.463 $\pm$ 72.023 & -43.941 $\pm$ 72.556 & 20.489 $\pm$ 6.138 & 396 \\
      \textbf{DEC (filtered)} & 81.795 $\pm$ 65.626 & -40.049 $\pm$ 55.112 & 19.888 $\pm$ 2.251 & 316 \\
    \end{tabular}
    \caption{Melotte 25 results.}
    \label{tab:results_melotte_25}
  \end{center}
\end{table}

@@

All of these clusters have a wide variety of diameters, from 25 to 330 arcmin,
as well as the number of stars that belong to them.
NGC 2682 has 3,000 stars while Melotte 25 is composed by more than 400,000 stars.
More information about the studied clusters is available in Table \ref{tab:clusters_summary}.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Open Cluster} & \emph{$\alpha$ J2000 $(degrees)$} & \emph{$\delta$ J2000 $(degrees)$} & \emph{Radius $(arcmin)$} & \emph{\# stars} \\
      \hline
      NGC 2516 & 119.517 & -60.753 & 15 & 12,869 \\
      NGC 2632 & 130.1 & 19.667 & 35 & 13,167 \\
      NGC 2682 & 132.825 & 11.8 & 12.5 & 2,839 \\
      Melotte 22 & 56.75 & 24.117 & 60 & 61,552 \\
      Melotte 25 & 66.725 & 15.867 & 165 & 433,996 \\
    \end{tabular}
    \caption{Righ ascension, declination, radius and number of stars of studied clusters.
             The number of stars corresponds to those stars contained within a cone of center
             $(\alpha, \delta)$ and raius the cluster's radius multiplied by a factor of 1.5.}
    \label{tab:clusters_summary}
  \end{center}
\end{table}

In all cases, the model has resolved properly the identity of the cluster
and has characterized the membership stars,
giving compatible results with the ones obtained with classic procedures and VO tools.

Compared with the mentioned tools, our model can be fully calified as a non-parameterized model
since it does not depend on parameters referred to the cluster itself
but only hyperparameters such as the initial number of clusters to be found,
or the structure of the Clustering Layer used by DEC model.

Our model is also non-supervised since we do not need to tell the model
which stars belong to the cluster or assit it while its training stage.

Only at the end of the characterization, a fine tuning driven by the user,
can be applied in order to improve the selection by discarding those
stars which fall outside the given quantiles.

In any case, we do not make assumptions about the cluster profile,
something that we have to take into account when using VO tools.
This is another evidence that our model is non-parameterized.

% TODO: Add references to figures and tables
